---
title: "Kevin Wang's template"
author: "Kevin Wang"
date: "`r paste0('Initiated on 2020 Aug 22, compiled on ', format(Sys.time(), '%Y %b %d'))`"
output:
  html_document:
    code_folding: hide
    fig_height: 12
    fig_width: 12
    toc: yes
    number_sections: true
    toc_depth: 3
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

# Summary

# Loading 

## packages
```{r}
library(tidyverse)
library(survminer)
library(survival)
library(patchwork)
library(ggsci)


theme_set(
  theme_classic(18) +
    theme(legend.position = "bottom", 
          panel.grid.minor = element_blank()))
```

## data

```{r}
clean_test_batting_inngings = readr::read_csv("data/clean_test_batting_inngings.csv") %>% 
  dplyr::mutate(runs_num = runs %>% stringr::str_extract("\\-*\\d+\\.*\\d*") %>% as.integer(),
                not_out = runs %>% stringr::str_detect("[*]"),
                dead = !not_out)

glimpse(clean_test_batting_inngings)
```

# Visualise KM plot for selected players
```{r}
selected_players = clean_test_batting_inngings %>% 
  dplyr::filter(player_name %in% c("MJ Clarke", "SPD Smith", "RT Ponting", "SR Waugh"))

selected_players_df =  selected_players %>% 
  dplyr::transmute(player_name, 
                   runs_num, 
                   dead) %>% 
  as.data.frame()

fit = survfit(Surv(runs_num, dead) ~ player_name, data = selected_players_df)

survminer::ggsurvplot(
  fit = fit, 
  data = selected_players_df, 
  pval = TRUE, palette = "Set1")
```


# Also make a survival plot for all players to verify the hypothesis that you are more likely to get out in the first 30 balls faced. 

```{r}
fit_bf = survfit(Surv(balls_faced, dead) ~ 1, data = clean_test_batting_inngings)

plot_bf = survminer::ggsurvplot(
  fit = fit_bf,
  data = clean_test_batting_inngings,
  palette = "Set1",
  surv.median.line = "hv")$plot + 
  labs(x = "Balls faced before getting out",
       title = "Balls faced survival plot") +
  scale_x_continuous(breaks = c(30, 100, 200, 400, 600, 800))
```



```{r, fig.height = 10, fig.width = 16}
fit_runs = survfit(Surv(runs_num, dead) ~ 1, data = clean_test_batting_inngings)

plot_runs = survminer::ggsurvplot(
  fit = fit_runs,
  data = clean_test_batting_inngings,
  palette = "Set1",
  surv.median.line = "hv")$plot +
  labs(x = "Runs scored before getting out",
       title = "Runs scored survival plot") +
  scale_x_continuous(breaks = c(30, 100, 200, 400, 600, 800))

plot_bf + plot_runs
```


# Logistic model 


The logic here is the following: we use the `out` as the binary response variable and `balls_faced` as the continuous predictor. We want to find out what are the chances that certain players get out after facing certain number of balls. 

```{r}
library(lme4)
library(sjPlot)

clean_test_batting_inngings_complete = clean_test_batting_inngings %>% 
  dplyr::mutate(dead = dead %>% as.integer) %>% 
  dplyr::filter(complete.cases(balls_faced), 
                complete.cases(runs_num),
                complete.cases(dead))

clean_test_batting_inngings_complete

M1 = glm(dead ~ runs_num + balls_faced + fours + sixes + pos + inns, 
         family = "binomial", data = clean_test_batting_inngings_complete)

M1 %>% summary

list_M1_plots = plot_model(M1, type = "eff")
patchwork::wrap_plots(list_M1_plots)
```


```{r}
pos_tbl = clean_test_batting_inngings_complete %>% 
  dplyr::filter(pos <= 10) %>% 
  dplyr::mutate(pos = factor(pos))

M2 = glm(dead ~ balls_faced * pos + mins * pos, 
         family = "binomial", data = pos_tbl)

summary(M2)

list_M2_plots = plot_model(M2, type = "int")
  # scale_colour_d3() +
  # scale_fill_d3()

list_M2_plots

list_M2_plots[[1]] + 
  scale_x_log10(limits = c(1, 400)) + 
  geom_vline(xintercept = 120, linetype = 2) +
  scale_colour_d3() +
  scale_fill_d3() +
  labs(x = "Balls faced before getting out", 
       y = "Prob. of getting out",
       colour = "Batting position")

# plot_model(M2, type = "int")[[2]] + scale_x_log10()
```



# Logistic mixed model on survival 

```{r, eval = FALSE}
M2 = glmer(dead ~ runs_num + balls_faced + fours + sixes + pos + inns + country + (1|player_name), 
         family = "binomial", data = clean_test_batting_inngings_complete)

M2 %>% summary
plot_model(M2, type = "eff")
```


# Session Info
```{r}
sessioninfo::session_info()
```

