---
title: "Kevin Wang's template"
author: "Kevin Wang"
date: "`r paste0('Initiated on 2020 Aug 22, compiled on ', format(Sys.time(), '%Y %b %d'))`"
output:
  html_document:
    code_folding: hide
    fig_height: 12
    fig_width: 12
    toc: yes
    number_sections: true
    toc_depth: 3
    toc_float: yes
    theme: paper
editor_options: 
  chunk_output_type: console
---

# Summary

# Loading 

## packages
```{r}
library(tidyverse)
library(sjPlot)
library(ggsci)

theme_set(
  theme_classic(18) +
    theme(legend.position = "bottom", 
          panel.grid.minor = element_blank()))
```

## functions
```{r}
clean_over_balls = function(x){
  x %>% 
    tidyr::separate(
      col = "ball", 
      into = c("over", "over_ball"), 
      sep = "[.]", remove = FALSE) %>% 
    dplyr::mutate(
      ball = as_factor(ball), 
      over = over %>% as.integer,
      over_ball = over_ball %>% as.integer(),
      wicket = ifelse(wicket_out %>% complete.cases, "yes", "no") %>% factor())
}
```


## data

```{r}
raw_tbl = readRDS("data/RData/ball_by_ball_22_Aug_2020.rds")
```


# Visualise single match

```{r}
test1 = raw_tbl %>% slice(1) %>% unnest(match_tbl) %>% unnest(innings_tbl) %>% 
  clean_over_balls

test1 %>% glimpse()

test1 %>% 
  ggplot(aes(x = over, y = runs_batsman,
             colour = wicket,
             alpha = wicket, 
             size = wicket)) +
  geom_point() +
  scale_y_continuous(breaks = 0:6) +
  scale_colour_brewer(palette = "Set1") +
  scale_alpha_manual(values = c("yes" = 1, "no" = 0.05)) +
  scale_size_manual(values = c("yes" = 3, "no" = 1)) +
  facet_wrap(~innings, scales = "free_x")
```


## NM Lyon

```{r}
lyon = test1 %>% 
  dplyr::filter(bowler == "NM Lyon")

lyon %>% 
  ggplot(aes(x = over, y = runs_batsman,
             colour = wicket,
             alpha = wicket, 
             size = wicket)) +
  geom_point() +
  scale_y_continuous(breaks = 0:6) +
  scale_colour_brewer(palette = "Set1") +
  scale_alpha_manual(values = c("yes" = 1, "no" = 0.5)) +
  scale_size_manual(values = c("yes" = 3, "no" = 1)) +
  facet_wrap(~innings, scales = "free_x")


lyon %>% 
  ggplot(aes(x = over_ball, y = runs_batsman,
             colour = wicket,
             alpha = wicket, 
             size = wicket)) +
  geom_point() +
  scale_y_continuous(breaks = 0:6) +
  scale_colour_brewer(palette = "Set1") +
  scale_alpha_manual(values = c("yes" = 1, "no" = 0.5)) +
  scale_size_manual(values = c("yes" = 3, "no" = 1)) +
  facet_wrap(~innings, scales = "free_x")
```

# Which ball is more likely to take wicket?

Maybe use a series of piecharts.
```{r}
test1 %>% 
  ggplot(aes(x = over_ball, y = runs_batsman,
             colour = wicket,
             alpha = wicket, 
             size = wicket)) +
  geom_point() +
  scale_y_continuous(breaks = 0:6) +
  scale_colour_brewer(palette = "Set1") +
  scale_alpha_manual(values = c("yes" = 1, "no" = 0.5)) +
  scale_size_manual(values = c("yes" = 3, "no" = 1)) +
  facet_wrap(~innings, scales = "free_x")
```

## Logistic model

```{r}
M1 = glm(wicket ~ over + factor(over_ball), family = "binomial", data = test1 %>% dplyr::filter(over_ball <= 6))
summary(M1)

plot_model(M1, type = "pred", digits = 4)
```

# Logistic model on all tests
```{r}
all_tests = raw_tbl %>% unnest(match_tbl) %>% 
  dplyr::mutate(total_balls_match = purrr::map_int(innings_tbl, nrow)) %>% 
  unnest(innings_tbl) %>% 
  clean_over_balls() %>% 
  dplyr::filter(over_ball <= 6)

M2 = glm(wicket ~ over + factor(over_ball), family = "binomial", data = all_tests)

summary(M2)

plot_model(M2, type = "pred", digits = 10)

# qqnorm(M$residuals)
# qqline(M$residuals)
```

# Linear mixed model 
```{r, eval = FALSE}
library(lme4)
M3 = glmer(wicket ~ over + factor(over_ball) + (1 | venue), 
           family = "binomial", data = all_tests)

plot_model(M3, type = "pred", digits = 4)
```

# Building pressure 

The hypothesis is that prior to taking wickets, batsmen are typically strangled to taking runs. 

The following visualise the runs before taking wicket.

```{r}
# cum_balls_before_wkt = purrr::map(.x = which(all_tests$wicket == "yes"), .f = ~ seq(.x, 0, by = -1))

where_wkts = which(all_tests$wicket == "yes")
cum_balls_before_wkt = rep(NA, length(all_tests$wicket))
last_wkt = 0
for(wkt in where_wkts){
  cum_balls_before_wkt[(last_wkt + 1L):wkt] = seq(wkt - last_wkt - 1L, 0L, by = -1)
  last_wkt = wkt
}

pressure = all_tests %>% 
  dplyr::mutate(
    cum_all_wkt = cumsum(wicket == "yes"),
    cum_balls_before_wkt = cum_balls_before_wkt) %>% 
  group_by(filename, batting_team, innings) %>% 
  dplyr::mutate(
    cum_inns_wkt = cumsum(wicket == "yes")) %>% 
  ungroup()

# View(pressure %>% slice(1:100))

pressure %>% 
  dplyr::filter(filename == "data/ball_by_ball_raw//1000851.yaml") %>%
  ggplot(aes(x = cum_balls_before_wkt, y = runs_total)) +
  geom_point(alpha = 0.5) + 
  scale_y_continuous(breaks = 0:6) +
  scale_x_continuous(trans = "log1p", breaks = c(0:18))

pressure_perc = pressure %>% 
  dplyr::filter(cum_balls_before_wkt <= 18) %>% 
  group_by(cum_balls_before_wkt, runs_total) %>% 
  dplyr::tally() %>% 
  dplyr::mutate(perc = n/sum(n)) %>% 
  ungroup()

pressure_perc %>% 
  ggplot(aes(x = cum_balls_before_wkt, 
             y = perc)) +
  geom_col(aes(fill = factor(runs_total))) +
  scale_fill_d3()

pressure_perc %>% 
  ggplot(aes(x = cum_balls_before_wkt, 
             y = perc, colour = factor(runs_total))) +
  geom_line(size = 1.5) +
  scale_colour_d3() +
  scale_x_continuous(breaks = c(1:10))
```


```{r}
bowler_pressure = pressure %>% 
  group_by(filename) %>% 
  dplyr::mutate(wkt_bowler = ifelse(wicket == "yes", bowler, NA)) %>% 
  tidyr::fill(wkt_bowler, .direction = "down") %>% 
  ungroup() %>% 
  group_by(wkt_bowler) %>% 
  nest() %>% 
  dplyr::mutate(total_balls = purrr::map_int(data, nrow))

bowler_pressure_perc = bowler_pressure %>% 
  dplyr::filter(complete.cases(wkt_bowler)) %>% 
  ungroup() %>% 
  # dplyr::filter(rank(desc(total_balls)) <= 50) %>%
  dplyr::filter(rank(desc(total_balls)) <= 11 | wkt_bowler == "SR Watson") %>%
  # dplyr::filter(rank(desc(total_balls)) <= 11 | wkt_bowler == "") %>%
  # dplyr::filter(wkt_bowler %in% c("JM Anderson", "NM Lyon")) %>%
  # dplyr::filter(rank(desc(total_balls)) <= 10) %>% 
  unnest(data) %>% 
  dplyr::filter(cum_balls_before_wkt <= 12, cum_balls_before_wkt > 0) %>% 
  group_by(wkt_bowler, cum_balls_before_wkt, runs_total) %>% 
  dplyr::tally() %>% 
  dplyr::mutate(perc = n/sum(n)) %>% 
  dplyr::filter(perc < 1) %>%
  ungroup()


bowler_pressure_perc %>%  
  ggplot(aes(x = cum_balls_before_wkt, 
             y = perc, 
             colour = factor(runs_total),
             group = interaction(runs_total, wkt_bowler)
             )) +
  geom_line(size = 0.5) +
  scale_colour_d3() +
  scale_x_continuous(breaks = c(0:12)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
  labs(x = "Num of runs before taking wicket", 
       y = "Percentage averaged across 12 balls", 
       colour = "Runs")

bowler_pressure_perc %>% 
  ggplot(aes(x = cum_balls_before_wkt, 
             y = perc)) +
  geom_col(aes(fill = factor(runs_total))) +
  geom_hline(yintercept = 0.25) +
  # geom_hline(yintercept = 0.12) +
  scale_fill_d3() +
  scale_x_continuous(breaks = c(0:12)) +
  facet_wrap(~wkt_bowler) +
  labs(x = "Num of runs before taking wicket", 
       y = "Percentage averaged across 12 balls", 
       fill = "Runs")
```



## What about the chance of a batsman facing the same bowler before taking a wicket

```{r}
pressure %>%
  group_by(cum_all_wkt) %>%
  summarise(
    wkt_taking_bowler = mean(unique(bowler) == last(bowler))) %>%
  ggplot(aes(x = wkt_taking_bowler)) +
  geom_histogram()




# M3 = glm(wicket ~ factor(over_ball) * cum_balls_before_wkt, family = "binomial", data = pressure)
#
# summary(M3)
```



# Session Info
```{r}
sessioninfo::session_info()
```

